---
title: 'STEPS Study: Objective 1'
author: "C. Konstantinou and X. Andrianou @ Water and Health Laboratory, CII-CUT"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmdformats::downcute:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
editor_options: 
  chunk_output_type: console
---



```{r,  echo=FALSE, include=FALSE}
rm(list=ls())


ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg))
    install.packages(new.pkg, dependencies = TRUE,
                     repos = "http://cran.us.r-project.org")
  sapply(pkg, require, character.only = TRUE)
}

# usage
packages <- c("tidyverse","lubridate","officer", "rvg","glue", "patchwork","janitor",
              "tableone", "readxl", "knitr")

ipak(packages)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

# read PA and MCF data
dataset_P_final <- readRDS("produced_data/dataset_P_final_forquestionnaires.rds", refhook = NULL) %>%   # this school needs to be excluded as classes and outdoor refer to 1st level and inclusion criteria were schools in ground floor 
  filter(SchoolID != "S25")
dataset_M_final <- readRDS("produced_data/dataset_M_final.rds", refhook = NULL) %>% 
  mutate(indoor_outdoor=case_when(location =="OD" ~ "outdoors",
                                  TRUE ~ "indoors")) %>% 
  select (-exclusion) %>% 
    # this school needs to be excluded as classes and outdoor refer to 1st level and inclusion criteria were schools in ground floor 
  filter(SchoolID != "S25")

# create exploratory table by creating new variables

datamanagement<- read.csv("rawData/datamanagement_2.csv", header= TRUE) %>%
  clean_names() %>%
  dplyr::rename(SchoolID=1) %>%
    filter(SchoolID != "S25") %>% 
  mutate(samplingday1date=as.POSIXct(samplingday1_date, format="%d/%m/%Y"),
         samplingday2date=as.POSIXct(samplingday2_date, format="%d/%m/%Y")) %>%
  mutate(samplingdays = as.factor(case_when(samplingday2_date == "" ~ "1",
                                  TRUE ~ "2")),
         settings = as.factor(case_when(data_c1_p == "X" & data_c2_p == "X" & 
                                data_od_p == "X" ~ "bothclasses_and_outdoor",
                              data_c1_p == "X" & data_c2_p == "X" & 
                                data_od_p != "X" ~ "bothclasses",
                              data_c1_p != "X" & data_c2_p == "X" & 
                                data_od_p != "X" ~ "oneclass",
                              data_c1_p == "X" & data_c2_p != "X" & 
                                data_od_p != "X" ~ "oneclass",
                              data_c1_p != "X" & data_c2_p == "X" & 
                                data_od_p == "X" ~ "oneclass_and_outdoor",
                              data_c1_p == "X" & data_c2_p != "X" & 
                                data_od_p == "X" ~ "oneclass_and_outdoor")),
         sampling_month = as.factor(case_when(samplingday1date >= "2021-05-01" & 
                                      samplingday1date < "2021-06-01" & 
                                      samplingday2date >= "2021-06-01" & 
                                      samplingday2date < "2021-07-01" ~ "May_June",
                                    samplingday1date >= "2021-05-01" & 
                                      samplingday1date < "2021-06-01" ~ "May",
                                    samplingday1date >= "2021-06-01" & 
                                      samplingday1date < "2021-07-01" ~ "June",
                                    samplingday1date >= "2021-07-01" & 
                                      samplingday1date < "2021-07-08" ~ "July"
                                    ))) %>% 
  select (-c(samplingday1_date,samplingday2_date))

#create variable for duration of sampling in each school location in each date

#duration <- questPA %>% 
#  group_by(EESTDateTime, SchoolID, location, PM) %>%
#  dplyr::summarise(duration = max(EESTDateTime) - min(EESTDateTime)) %>%
#  group_by(SchoolID, location) %>%
#  summarise(duration_S = sum(duration, na.rm = TRUE))

```


# Summary Tables

`r kable(print(CreateTableOne(vars = c("samplingdays", "settings","sampling_month"), data = datamanagement)), caption="Schools data summary collection") `

```{r, echo=FALSE, message=FALSE, warning=FALSE}

table_PA_indooroutdoor <- dataset_P_final %>% 
  group_by(indoor_outdoor, PM) %>% 
  dplyr::summarise(n=n(),
                   mean=round(mean(final_value, na.rm=TRUE), digits=1),
                   sd=round(sd(final_value, na.rm=TRUE), digits=1),
                   min=round(min(final_value, na.rm=TRUE), digits=1),
                   p25=round(quantile(final_value, probs=0.25, na.rm=TRUE), digits=1),
                   median=round(median(final_value, na.rm=TRUE), digits=1),
                   p75=round(quantile(final_value, probs=0.75, na.rm=TRUE), digits=1),
                   max=round(max(final_value, na.rm=TRUE), digits=1), .groups="drop")

table_MCF_indooroutdoor <- dataset_M_final %>% 
  group_by(indoor_outdoor, name) %>% 
  dplyr::summarise(n=n(),
                   mean=round(mean(value, na.rm=TRUE), digits=1),
                   sd=round(sd(value, na.rm=TRUE), digits=1),
                   min=round(min(value, na.rm=TRUE), digits=1),
                   p25=round(quantile(value, probs=0.25, na.rm=TRUE), digits=1),
                   median=round(median(value, na.rm=TRUE), digits=1),
                   p75=round(quantile(value, probs=0.75, na.rm=TRUE), digits=1),
                   max=round(max(value, na.rm=TRUE), digits=1), .groups="drop")

table_PA_district_indooroutdoor <- dataset_P_final %>% 
  group_by(district, indoor_outdoor, PM) %>% 
  dplyr::summarise(n=n(),
                   mean=round(mean(final_value, na.rm=TRUE), digits=1),
                   sd=round(sd(final_value, na.rm=TRUE), digits=1),
                   min=round(min(final_value, na.rm=TRUE), digits=1),
                   p25=round(quantile(final_value, probs=0.25, na.rm=TRUE), digits=1),
                   median=round(median(final_value, na.rm=TRUE), digits=1),
                   p75=round(quantile(final_value, probs=0.75, na.rm=TRUE), digits=1),
                   max=round(max(final_value, na.rm=TRUE), digits=1), .groups="drop")

table_MCF_district_indooroutdoor <- dataset_M_final %>% 
  group_by(district, indoor_outdoor, name) %>% 
  dplyr::summarise(n=n(),
                   mean=round(mean(value, na.rm=TRUE), digits=1),
                   sd=round(sd(value, na.rm=TRUE), digits=1),
                   min=round(min(value, na.rm=TRUE), digits=1),
                   p25=round(quantile(value, probs=0.25, na.rm=TRUE), digits=1),
                   median=round(median(value, na.rm=TRUE), digits=1),
                   p75=round(quantile(value, probs=0.75, na.rm=TRUE), digits=1),
                   max=round(max(value, na.rm=TRUE), digits=1), .groups="drop")

table_PA_district_degurba_indooroutdoor <- dataset_P_final %>% 
  group_by(district, degurba, indoor_outdoor, PM) %>% 
  dplyr::summarise(n=n(),
                   mean=round(mean(final_value, na.rm=TRUE), digits=1),
                   sd=round(sd(final_value, na.rm=TRUE), digits=1),
                   min=round(min(final_value, na.rm=TRUE), digits=1),
                   p25=round(quantile(final_value, probs=0.25, na.rm=TRUE), digits=1),
                   median=round(median(final_value, na.rm=TRUE), digits=1),
                   p75=round(quantile(final_value, probs=0.75, na.rm=TRUE), digits=1),
                   max=round(max(final_value, na.rm=TRUE), digits=1), .groups="drop")

table_MCF_district_degurba_indooroutdoor <- dataset_M_final %>% 
  group_by(district, degurba, name, indoor_outdoor) %>% 
  dplyr::summarise(n=n(),
                   mean=round(mean(value, na.rm=TRUE), digits=1),
                   sd=round(sd(value, na.rm=TRUE), digits=1),
                   min=round(min(value, na.rm=TRUE), digits=1),
                   p25=round(quantile(value, probs=0.25, na.rm=TRUE), digits=1),
                   median=round(median(value, na.rm=TRUE), digits=1),
                   p75=round(quantile(value, probs=0.75, na.rm=TRUE), digits=1),
                   max=round(max(value, na.rm=TRUE), digits=1), .groups="drop")
            
```

`r DT::datatable(table_PA_indooroutdoor, caption="PA data (indoor-outdoor comparison)")`

`r DT::datatable(table_MCF_indooroutdoor, caption = "MCF data (indoor-outdoor comparison)")`

`r DT::datatable(table_PA_district_indooroutdoor, caption = "PA data (district, indoor-outdoor comparison)")`

`r DT::datatable(table_MCF_district_indooroutdoor, caption = "MCF data (district, indoor-outdoor comparison)")`

`r DT::datatable(table_PA_district_degurba_indooroutdoor, caption = "PA data (district,degurba indoor-outdoor comparison)")`

`r DT::datatable(table_MCF_district_degurba_indooroutdoor, caption = "MCF data (district, degurba, indoor-outdoor comparison)")`

# Plots - indoors vs outdoors 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# check the raw values plots 

dataset_P_final %>% 
  filter(PM == "pm1_0") %>%
  ggplot() +
  geom_point(aes(x=EESTDateTime, y=final_value, colour = location), shape = 21, alpha = 0.5, size = 2) +  facet_wrap(~indoor_outdoor, ncol=1) +
  scale_color_brewer(palette="Dark2") +
theme_minimal() +
   theme(legend.position="bottom") +
  labs(y = "PM1 (ug/m3)", x = "")

dataset_P_final %>% 
  filter(PM == "pm10_0") %>%
  ggplot() +
  geom_point(aes(x=EESTDateTime, y=final_value, colour = location), shape = 21, alpha = 0.5, size = 2) +  facet_wrap(~indoor_outdoor, ncol=1) +
  scale_color_brewer(palette="Dark2") +
theme_minimal() +
   theme(legend.position="bottom") +
  labs(y = "PM10 (ug/m3)", x = "Date")

dataset_P_final %>% 
  ggplot() +
  geom_point(aes(x=EESTDateTime, y=final_value, colour = location), shape = 21, alpha = 0.5, size = 2) +  facet_wrap(~indoor_outdoor, ncol=1) +
  scale_color_brewer(palette="Dark2") +
theme_minimal() +
   theme(legend.position="bottom") +
  labs(y = "PM2.5 (ug/m3)", x = "Date")

dataset_M_final %>% 
    filter(name == "temperature") %>%
  ggplot() +
  geom_point(aes(x=time, y=value, colour = location), shape = 21, alpha = 0.5, size = 2) +  facet_wrap(~indoor_outdoor, ncol=1) +
  scale_color_brewer(palette="Dark2") +
theme_minimal() +
   theme(legend.position="bottom") +
  labs(y = "Temperature (C)", x = "Date")

dataset_M_final %>% 
    filter(name == "humidity") %>%
  ggplot() +
  geom_point(aes(x=time, y=value, colour = location), shape = 21, alpha = 0.5, size = 2) +  facet_wrap(~indoor_outdoor, ncol=1) +
  scale_color_brewer(palette="Dark2") +
theme_minimal() +
   theme(legend.position="bottom") +
  labs(y = "Rel.Humidity (%)", x = "Date")


dataset_M_final %>% 
    filter(name == "carbon_dioxide") %>%
  ggplot() +
  geom_point(aes(x=time, y=value, colour = location), shape = 21, alpha = 0.5, size = 2) +  facet_wrap(~indoor_outdoor, ncol=1) +
  scale_color_brewer(palette="Dark2") +
theme_minimal() +
   theme(legend.position="bottom") +
  labs(y = "Carbon dioxide (ppm)", x = "Date")


dataset_M_final %>% 
    filter(name == "b_voc") %>%
  ggplot() +
  geom_point(aes(x=time, y=value, colour = location), shape = 21, alpha = 0.5, size = 2) +  facet_wrap(~indoor_outdoor, ncol=1) +
  scale_color_brewer(palette="Dark2") +
theme_bw() +
   theme(legend.position="bottom") +
  labs(y = "VOCs (ppb)", x = "Date")

```


# Plots for each school - PA data

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# for the PA data

SchoolID_levels_PA <- levels(as.factor(dataset_P_final$SchoolID))

for(i in 1:length(SchoolID_levels_PA)){
  
  temp_school <- dataset_P_final %>% 
  filter(SchoolID==SchoolID_levels_PA[i]) 
   
  schoolplot <- ggplot(temp_school) +
    geom_point(aes(x=EESTDateTime, y=final_value, colour = location), shape = 21, alpha = 0.5, size = 2) +
    geom_smooth(aes(x=EESTDateTime, y=final_value, color=location), method="loess", span=0.1, se = F) +
    scale_color_brewer(palette="Dark2") +
    theme_bw() +
     theme(legend.position="bottom") +
    facet_wrap(~PM, ncol=1) +
    labs(y = "PM (ug/m3)", x = NULL, 
         caption = glue("PM (ug/m3) raw values indoors and outdoors in {SchoolID_levels_PA[i]}"))
  
  print(schoolplot)
  rm(schoolplot, temp_school)
  
}

rm(SchoolID_levels_PA)
```

# Plots for each school - MCF data

```{r, echo=FALSE, message=FALSE, warning=FALSE}

SchoolID_levels_MCF <- levels(as.factor(dataset_M_final$SchoolID))

temp_M_forplots <- dataset_M_final%>%
    filter(name!= "voc_loess") %>% 
  mutate(label_for_plot=case_when(name=="b_voc"~"VOCs (ppb)",
                                  name=="carbon_dioxide"~"CO2 (ppm)",
                                  name=="humidity"~"Humidity (%)",
                                  name=="temperature"~"Temperature (C)"))

for(i in 1:length(SchoolID_levels_MCF)){
  
  temp_school <- temp_M_forplots %>% 
  filter(SchoolID==SchoolID_levels_MCF[i]) 
 
  
  schoolplot <- ggplot(temp_school) +
  geom_point(aes(x=time, y=value, colour = location), shape = 21, alpha = 0.5, size = 2) +
  geom_smooth(aes(x=time, y=value, color=location), method="loess", span=0.1, se = F) +
  scale_color_brewer(palette="Dark2") +
    facet_wrap(~label_for_plot, ncol=1, scales = "free_y")+
    theme_bw() +
     theme(legend.position="bottom") +
    labs(y = NULL, x = NULL, 
         caption = glue("Raw values indoors and outdoors in {SchoolID_levels_MCF[i]}"))
  
  print(schoolplot)
  rm(schoolplot, temp_school)
  
}

```

# Session Information

```{r S3 }
sessionInfo()
```
