---
title: " STEPS Study: Objective 2 - Comparison indoors and outdoors (regression analysis)"
author: "C. Konstantinou and X. Andrianou @ Water and Health Laboratory, CII-CUT"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmdformats::downcute:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
editor_options: 
  chunk_output_type: console
---


```{r packages,  echo=FALSE, include=FALSE}
rm(list=ls())


ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg))
    install.packages(new.pkg, dependencies = TRUE,
                     repos = "http://cran.us.r-project.org")
  sapply(pkg, require, character.only = TRUE)
}

# usage
packages <- c("tidyverse","lubridate","officer", "rvg","glue", "patchwork","janitor",
              "tableone","dplyr","lme4","readxl","scales","sjPlot","sjmisc")

ipak(packages)
```

```{r readdata, echo=FALSE, message=FALSE, warning=FALSE}

# read data

# period mean - only school
dataset_final_regression_onlysch <- readRDS("produced_data/dataset_final_regression_onlysch.rds", refhook = NULL) %>% 
  mutate(period=as.numeric(period_new)) %>% 
droplevels() 

dataset_final_regression_excl_onlysch <- readRDS("produced_data/dataset_final_regression_excl_onlysch.rds", refhook = NULL) %>% 
  droplevels() %>% 
  mutate(period=as.numeric(period_new))

dataset_final_regression_onlysch_M <- readRDS("produced_data/dataset_final_regression_onlysch_M.rds", refhook = NULL) %>% 
  droplevels() %>% 
  mutate(period=as.numeric(period_new))

dataset_final_regression_onlysch_excl_M <- readRDS("produced_data/dataset_final_regression_excl_onlysch_M.rds", refhook = NULL) %>% 
  droplevels() %>% 
  mutate(period=as.numeric(period_new))

```


```{r regression_datasets, echo = FALSE, message=FALSE, warning=FALSE}

#EXCLUSIONS DATASET

# final dataset for PM1
dataset_PM1_final_regression_excl <- dataset_final_regression_excl_onlysch %>% 
  filter(name=="pm1_0") %>% 
  dplyr::rename(pm1_mean_indoors=mean_indoors,
                pm1_mean_outdoors=mean_outdoors)

# final dataset for PM2.5
dataset_PM2_5_final_regression_excl <- dataset_final_regression_excl_onlysch %>% 
  filter(name=="pm2_5") %>% 
  dplyr::rename(pm2_5_mean_indoors=mean_indoors,
                pm2_5_mean_outdoors=mean_outdoors)

# final dataset for PM10
dataset_PM10_final_regression_excl <- dataset_final_regression_excl_onlysch %>% 
  filter(name=="pm10_0") %>% 
    dplyr::rename(pm10_mean_indoors=mean_indoors,
                pm10_mean_outdoors=mean_outdoors)

# final dataset for temperature
dataset_temp_final_regression_excl <- dataset_final_regression_onlysch_excl_M %>% 
  filter(name=="temperature") %>% 
    dplyr::rename(temp_mean_indoors=mean_indoors,
                temp_mean_outdoors=mean_outdoors) 

# final dataset for rel. humidity
dataset_hum_final_regression_excl <- dataset_final_regression_onlysch_excl_M %>% 
  filter(name=="humidity") %>% 
  dplyr::rename(hum_mean_indoors=mean_indoors,
                hum_mean_outdoors=mean_outdoors) 

# dataset for temperature including humidity indoor
dataset_hum_excl <- dataset_hum_final_regression_excl %>% 
select(hum_mean_indoors,hum_mean_outdoors, SchoolID, location, samplingdate, period_new)

dataset_temp_hum_excl <- dataset_temp_final_regression_excl %>% 
  left_join(., select(dataset_hum_excl, hum_mean_indoors,hum_mean_outdoors, SchoolID, location, samplingdate, period_new))

# dataset combining PM data and humidity, temperature data
dataset_pm10_excl <- dataset_PM10_final_regression_excl %>% 
select(pm10_mean_indoors,pm10_mean_outdoors, SchoolID, location, samplingdate, period_new)

dataset_pm1_excl <- dataset_PM1_final_regression_excl  %>% 
select(pm1_mean_indoors,pm1_mean_outdoors, SchoolID, location, samplingdate, period_new)

dataset_pm_temp_excl <- dataset_PM2_5_final_regression_excl %>% 
  left_join(., select(dataset_pm10_excl, pm10_mean_indoors, pm10_mean_outdoors, SchoolID, location, samplingdate, period_new)) %>% 
  left_join(., select(dataset_pm1_excl, pm1_mean_indoors, pm1_mean_outdoors, SchoolID, location, samplingdate, period_new)) %>% 
  left_join(., select(dataset_temp_hum_excl, hum_mean_indoors, hum_mean_outdoors, 
                      temp_mean_indoors, temp_mean_outdoors,SchoolID, 
                      location, samplingdate, period_new))

# final dataset for CO2
dataset_CO2_final_regression_excl <- dataset_final_regression_onlysch_excl_M %>% 
  filter(name=="carbon_dioxide") %>% 
   dplyr::rename(CO2_mean_indoors=mean_indoors,
                CO2_mean_outdoors=mean_outdoors)

# final dataset for VOC
dataset_VOC_final_regression_excl <- dataset_final_regression_onlysch_excl_M %>% 
  filter(name=="b_voc") %>% 
   dplyr::rename(VOCs_mean_indoors=mean_indoors,
                VOCs_mean_outdoors=mean_outdoors)

```

# Main Analysis

## Only school hours (excluding problematic classes)

Parameter (indoor) ~ Parameter (outdoor) + time_type (class as reference) + period + %windows_open + no of open fans + no of open doors + (1|SchoolID/location) 

```{r models_1_excL, echo = FALSE, message=FALSE, warning=FALSE}

PM1_model_ex <- lmer(formula = pm1_mean_indoors ~ pm1_mean_outdoors + temp_mean_indoors + hum_mean_indoors + time_type + period + percent_open_new + percent_open_new_fans + percent_open_new_doors + paint_indoors + chlorinefreq + (1|SchoolID:location), data=dataset_pm_temp_excl)

PM2_5_model_ex <- lmer(formula = pm2_5_mean_indoors ~ pm2_5_mean_outdoors + temp_mean_indoors + hum_mean_indoors + time_type + period + percent_open_new + percent_open_new_fans + percent_open_new_doors + paint_indoors + chlorinefreq + (1|SchoolID:location), data=dataset_pm_temp_excl)

PM10_model_ex <- lmer(formula = pm10_mean_indoors ~ pm10_mean_outdoors + temp_mean_indoors + hum_mean_indoors + time_type + period + percent_open_new + percent_open_new_fans + percent_open_new_doors + paint_indoors + chlorinefreq + (1|SchoolID:location), data=dataset_pm_temp_excl)

sjPlot::tab_model(PM1_model_ex, PM2_5_model_ex,PM10_model_ex, title ="PM (school hours excl. probl. classes)", p.style = "stars",digits = 3, collapse.ci = TRUE)

sjPlot::tab_model(PM1_model_ex, PM2_5_model_ex,PM10_model_ex, title ="PM (school hours excl. probl. classes)", collapse.ci = TRUE, p.style = "stars",digits = 3)

temp_model_ex <- lmer(formula = temp_mean_indoors ~ temp_mean_outdoors + hum_mean_indoors + time_type + period + percent_open_new + percent_open_new_fans + percent_open_new_doors + paint_indoors + chlorinefreq + (1|SchoolID:location), data=dataset_temp_hum_excl)

hum_model_ex <- lmer(formula = hum_mean_indoors ~ hum_mean_outdoors + temp_mean_indoors + time_type + period + percent_open_new + percent_open_new_fans + percent_open_new_doors + paint_indoors + chlorinefreq + (1|SchoolID:location), data=dataset_temp_hum_excl)

CO2_log_model_ex <- lmer(formula = log(CO2_mean_indoors) ~ log(CO2_mean_outdoors) + time_type + period + percent_open_new + percent_open_new_fans + percent_open_new_doors + paint_indoors + chlorinefreq + (1|SchoolID:location), data=dataset_CO2_final_regression_excl)

VOC_log_model_ex <- lmer(formula = log(VOCs_mean_indoors) ~ log(VOCs_mean_outdoors) + time_type + period + percent_open_new + percent_open_new_fans + percent_open_new_doors + paint_indoors + chlorinefreq + (1|SchoolID:location), data=dataset_VOC_final_regression_excl)

sjPlot::tab_model(temp_model_ex, hum_model_ex, CO2_log_model_ex, VOC_log_model_ex, title ="MCF outcomes (school hours excl. probl. classes)", p.style = "stars",digits = 3, collapse.ci = TRUE)


```

## Simple models - comparison of indoors and outdoors

### Only school hours (excluding problematic classes)
Parameter (indoor) ~ Parameter (outdoor) + (1|SchoolID/location) 

```{r models_1_excL_simple, echo = FALSE, message=FALSE, warning=FALSE}

PM1_model_ex_s <- lmer(formula = pm1_mean_indoors ~ pm1_mean_outdoors + (1|SchoolID:location), data=dataset_PM1_final_regression_excl)

PM2_5_model_ex_s <- lmer(formula = pm2_5_mean_indoors ~ pm2_5_mean_outdoors + (1|SchoolID:location), data=dataset_PM2_5_final_regression_excl)

PM10_model_ex_s <- lmer(formula = pm10_mean_indoors ~ pm10_mean_outdoors + (1|SchoolID:location), data=dataset_PM10_final_regression_excl)


sjPlot::tab_model(PM1_model_ex_s, PM2_5_model_ex_s, PM10_model_ex_s, title ="PM (school hours excl. probl. classes)", p.style = "stars",digits = 3, collapse.ci = TRUE)



temp_model_ex_s <- lmer(formula = temp_mean_indoors ~ temp_mean_outdoors + (1|SchoolID:location), data=dataset_temp_final_regression_excl)

hum_model_ex_s <- lmer(formula = hum_mean_indoors ~ hum_mean_outdoors + (1|SchoolID:location), data=dataset_hum_final_regression_excl)

CO2_log_model_ex_s <- lmer(formula = log(CO2_mean_indoors) ~ log(CO2_mean_outdoors) + (1|SchoolID:location), data=dataset_CO2_final_regression_excl)

VOC_log_model_ex_s <- lmer(formula = log(VOCs_mean_indoors) ~ log(VOCs_mean_outdoors) + (1|SchoolID:location), data=dataset_VOC_final_regression_excl)

sjPlot::tab_model(temp_model_ex_s,hum_model_ex_s,CO2_log_model_ex_s,VOC_log_model_ex_s, title ="MCF (school hours excl. probl. classes)", p.style = "stars",digits = 3, collapse.ci = TRUE)


```

# Sensitivity analysis

```{r regression_datasets_sensitiv, echo = FALSE, message=FALSE, warning=FALSE}

rm(list = setdiff(ls(), c("packages","ipak")))

dataset_final_regression_probandnorm <- readRDS("produced_data/dataset_final_regression_probandnorm.rds", refhook = NULL) %>% 
  filter(period_new!="bef_classes") %>% 
  filter(period_new!="after_classes") %>% 
    filter(class_type=="problematic") %>% 
  mutate(period=as.numeric(period_new)) %>% 
  droplevels() 

dataset_final_regression_M_probandnorm <- readRDS("produced_data/dataset_final_regression_M_probandnorm.rds", refhook = NULL) %>% 
  filter(period_new!="bef_classes") %>% 
  filter(period_new!="after_classes") %>% 
  filter(class_type=="problematic") %>% 
  mutate(period=as.numeric(period_new)) %>% 
  droplevels() 

# final dataset for PM1
dataset_PM1_final_regression_prob <- dataset_final_regression_probandnorm %>% 
  filter(name=="pm1_0") %>% 
  dplyr::rename(pm1_mean_indoors=mean_indoors,
                pm1_mean_outdoors=mean_outdoors) 

# final dataset for PM2.5
dataset_PM2_5_final_regression_prob <- dataset_final_regression_probandnorm %>% 
  filter(name=="pm2_5") %>% 
  dplyr::rename(pm2_5_mean_indoors=mean_indoors,
                pm2_5_mean_outdoors=mean_outdoors)

# final dataset for PM10
dataset_PM10_final_regression_prob <- dataset_final_regression_probandnorm %>% 
  filter(name=="pm10_0") %>% 
  dplyr::rename(pm10_mean_indoors=mean_indoors,
                pm10_mean_outdoors=mean_outdoors)

# final dataset for temperature
dataset_temp_final_regression_prob <- dataset_final_regression_M_probandnorm %>% 
  filter(name=="temperature") %>%
  dplyr::rename(temp_mean_indoors=mean_indoors,
                temp_mean_outdoors=mean_outdoors)

# final dataset for rel. humidity
dataset_hum_final_regression_prob <- dataset_final_regression_M_probandnorm %>% 
  filter(name=="humidity") %>% 
  dplyr::rename(hum_mean_indoors=mean_indoors,
                hum_mean_outdoors=mean_outdoors)

# dataset for temperature including humidity indoor
dataset_hum_prob <- dataset_hum_final_regression_prob  %>% 
select(hum_mean_indoors,hum_mean_outdoors, SchoolID, location, samplingdate, period_new)

dataset_temp_hum_prob <- dataset_temp_final_regression_prob  %>% 
  left_join(., select(dataset_hum_prob, hum_mean_indoors,hum_mean_outdoors, SchoolID, location, samplingdate, period_new))

# dataset combining PM data and humidity, temperature data
dataset_pm10_prob <- dataset_PM10_final_regression_prob  %>% 
select(pm10_mean_indoors,pm10_mean_outdoors, SchoolID, location, samplingdate, period_new)

dataset_pm1_prob <- dataset_PM1_final_regression_prob %>% 
select(pm1_mean_indoors,pm1_mean_outdoors, SchoolID, location, samplingdate, period_new)

dataset_pm_temp_prob <- dataset_PM2_5_final_regression_prob  %>% 
  left_join(., select(dataset_pm10_prob, pm10_mean_indoors, pm10_mean_outdoors, SchoolID, location, samplingdate, period_new)) %>% 
  left_join(., select(dataset_pm1_prob, pm1_mean_indoors, pm1_mean_outdoors, SchoolID, location, samplingdate, period_new)) %>% 
  left_join(., select(dataset_temp_hum_prob, hum_mean_indoors, hum_mean_outdoors, 
                      temp_mean_indoors, temp_mean_outdoors,SchoolID, 
                      location, samplingdate, period_new))

# final dataset for CO2
dataset_CO2_final_regression_prob <- dataset_final_regression_M_probandnorm %>% 
  filter(name=="carbon_dioxide") %>% 
  dplyr::rename(CO2_mean_indoors=mean_indoors,
                CO2_mean_outdoors=mean_outdoors)

# final dataset for bVOC
dataset_VOC_final_regression_prob <- dataset_final_regression_M_probandnorm %>% 
  filter(name=="b_voc") %>% 
  dplyr::rename(VOCs_mean_indoors=mean_indoors,
                VOCs_mean_outdoors=mean_outdoors)

```

## Only school hours (only problematic classes)

Parameter (indoor) ~ Parameter (outdoor) + time_type (class as reference) + period + %windows_open + no of open fans + no of open doors + (1|SchoolID/location) 

```{r models_onlyschhours, echo = FALSE, message=FALSE, warning=FALSE}

PM1_model_prob <- lmer(formula = pm1_mean_indoors ~ pm1_mean_outdoors + temp_mean_indoors + hum_mean_indoors + time_type + period + percent_open_new + percent_open_new_fans + percent_open_new_doors + paint_indoors + chlorinefreq + (1|SchoolID:location), data=dataset_pm_temp_prob )

PM2_5_model_prob <- lmer(formula = pm2_5_mean_indoors ~ pm2_5_mean_outdoors + temp_mean_indoors + hum_mean_indoors + time_type + period + percent_open_new + percent_open_new_fans + percent_open_new_doors + paint_indoors + chlorinefreq + (1|SchoolID:location), data=dataset_pm_temp_prob )

PM10_model_prob <- lmer(formula = pm10_mean_indoors ~ pm10_mean_outdoors + temp_mean_indoors + hum_mean_indoors + time_type + period + percent_open_new + percent_open_new_fans + percent_open_new_doors + paint_indoors + chlorinefreq + (1|SchoolID:location), data=dataset_pm_temp_prob )


sjPlot::tab_model(PM1_model_prob,PM2_5_model_prob,PM10_model_prob, title ="PM (school hours) - only problematic classes", p.style = "stars",digits = 3, collapse.ci = TRUE)



temp_model_prob <- lmer(formula = temp_mean_indoors ~ temp_mean_outdoors + hum_mean_indoors + time_type + period + percent_open_new + percent_open_new_fans + percent_open_new_doors + paint_indoors + chlorinefreq + (1|SchoolID:location), data=dataset_temp_hum_prob)

hum_model_prob <- lmer(formula = hum_mean_indoors ~ hum_mean_outdoors + temp_mean_indoors + time_type + period + percent_open_new + percent_open_new_fans + percent_open_new_doors + paint_indoors + chlorinefreq + (1|SchoolID:location), data=dataset_temp_hum_prob )

CO2_log_model_prob <- lmer(formula = log(CO2_mean_indoors) ~ log(CO2_mean_outdoors) + time_type + period + percent_open_new + percent_open_new_fans + percent_open_new_doors + paint_indoors + chlorinefreq + (1|SchoolID:location), data=dataset_CO2_final_regression_prob )

VOC_log_model_prob <- lmer(formula = log(VOCs_mean_indoors) ~ log(VOCs_mean_outdoors) + time_type + period + percent_open_new + percent_open_new_fans + percent_open_new_doors + paint_indoors + chlorinefreq + (1|SchoolID:location), data=dataset_VOC_final_regression_prob)

sjPlot::tab_model(temp_model_prob,hum_model_prob,CO2_log_model_prob,VOC_log_model_prob, title ="MCF outcomes (school hours) - only problematic classes", p.style = "stars",digits = 3, collapse.ci = TRUE)


```

# Session Information

```{r S8 }
sessionInfo()
```